Acceleration of Derivative Calculations with Application to Radial Basis Function -- Finite-Differences on the Intel MIC Architecture

### 2014-01-17 acm/ieee_paper.tex
scaling figure

\def\red#1{\textbf{\textcolor{red}{#1}}}
\def\blue#1{\textbf{\textcolor{blue}{#1}}}
\def\green#1{\textbf{\textcolor{green}{#1}}}
\def\qes#1{{\blue{*** For Erik: #1 ***}}}
\def\es#1{{\blue{*** For Erik: #1 ***}}}
\def\ee#1{{\green{#1}}}
\def\ge#1{{\blue{#1}}}
\def\NOTE#1{{\red{NOTE: #1}}}
\def\ttt#1{{\tt #1}}
\def\bold#1{{\bf #1}}

@@

\begin{figure*}
  \centering
\subfigure[Source code]{\includegraphics[clip=true,trim=4.5cm 11cm 4cm 4.2cm,width=.6\linewidth]{figures/code.pdf}}%
\subfigure[Content of the vector registers \ge{in the source code in (a)}.]{\hspace{-0.07\linewidth}\includegraphics[width=.5\linewidth]{figures/code-annote.pdf}}

>>>>

\def\red#1{\textbf{\textcolor{red}{#1}}}
\def\blue#1{\textbf{\textcolor{blue}{#1}}}
\def\green#1{\textbf{\textcolor{green}{#1}}}
\def\qes#1{{\blue{*** For Erik: #1 ***}}}
\def\es#1{{\blue{*** For Erik: #1 ***}}}
\def\ee#1{{\green{#1}}}
\def\ge#1{{\blue{#1}}}
%\def\NOTE#1{{\red{NOTE: #1}}}
\def\NOTE#1{{}}
\def\ttt#1{{\tt #1}}
\def\bold#1{{\bf #1}}

@@

\begin{figure*}
  \centering
\scalebox{.8}{
\subfigure[Source code]{\includegraphics[clip=true,trim=4.5cm 11cm 4cm 4.2cm,width=.6\linewidth]{figures/code.pdf}}%
\subfigure[Content of the vector registers \ge{in the source code in (a)}.]{\hspace{-0.07\linewidth}\includegraphics[width=.5\linewidth]{figures/code-annote.pdf}}
}
